Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-26 Markdown Documents/Manuscript.Rmd
small changes

Wildfire smoke is a mixture of many gasses aerated by biomass combustion across a landscape [@naeher_woodsmoke_2007]. While many of these compounds have been shown to cause health problems in humans, organic carbon and black carbon particulate matter less than 2.5 μm in diameter (PM2.5) is particularly harmful to human health, causing between 260,000 - 600,000 global deaths annually [@johnston_fay_h_estimated_2012; @naeher_woodsmoke_2007]. Health concerns regarding wildfire smoke, specifically PM2.5, regurlarly drive calls for individuals to reduce outdoor recreation behavior [@oneill_summary_2013].

>>>>

Wildfire smoke is a mixture of many gasses aerated by biomass combustion across a landscape [@naeher_woodsmoke_2007]. While many of these compounds have been shown to cause health problems in humans, organic carbon and black carbon particulate matter less than 2.5 μm in diameter (PM2.5) is particularly harmful to human health, causing between 260,000 - 600,000 global deaths annually [@johnston_fay_h_estimated_2012; @naeher_woodsmoke_2007]. Health concerns regarding wildfire smoke, specifically PM2.5, regularly drive calls for individuals to reduce outdoor recreation behavior [@oneill_summary_2013].
